%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                   Introduction                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{introduction}

%\authorcomment1{Start with a few sentences about coronal heating; move into short discussion on frequency; then discuss how frequency might be diagnosed with lots of background on previous studies of heating frequency in active regions; Provide some background on the timelag method; how does this help us understand the heating frequency?}

\authorcomment2{Need a few lead-in sentences here.} First proposed by \citet{parker_nanoflares_1988}, nanoflare heating provides a possible mechanism for heating the solar corona through small-scale, bursty energy release. Though originally pertaining to energetic events on the order $10^{24}$ erg due to small-scale reconnection, the term \textit{nanoflare} is now synonymous with any impulsive energy release and is not specific to any particular mechanism \citep{klimchuk_key_2015}. 

%\authorcomment1{Hot plasma possible signature; evidence from EUNIS, FOXSI, Parenti; but hot plasma difficult to detect, see Winebarger, Barnes, others?; cool slopes and timelags as an alternative though more indirect signatures of nanoflares}

While nanoflares remain a viable coronal heating mechanism, identifying observational signatures of impulsive heating events is non-trivial. One such signature is the presence of 8-10 MK plasma in non-flaring active regions, the so-called ``smoking gun'' of nanoflare heating \citep{cargill_implications_1994}. Unfortunately, due to its faint, transient nature, a positive detection of this hot plasma is made difficult by several factors \citep{winebarger_defining_2012,barnes_inference_2016}. However, recent observations of this very hot plasma have provided compelling evidence for the existence of nanoflares \citep[e.g.][]{reale_evidence_2009,schmelz_hinode_2009,testa_hinode/eis_2012,brosius_pervasive_2014,caspi_new_2015,parenti_spectroscopy_2017,ishikawa_detection_2017}. \authorcomment2{Maybe expand a bit on a few of these papers}.

Observations provide critical information for constraining nanoflare heating properties. One property of particular interest is the nanoflare \textit{frequency}, or the rate at which individual events occur on a given coronal strand. In the case of \textit{low-frequency} nanoflares, the time between consecutive events on a given strand is long relative to a characteristic loop cooling time, giving the loop time to fully cool and drain before the next event begins. In the \textit{high-frequency} scenario, the time between events is short relative to the cooling time such that the loop is not allowed to fully cool before being reheated. Steady heating may be regarded as nanoflare heating in the very high-frequency limit. Additional details regarding the parameterization of the heating frequency are given in \autoref{heating}. In addition to the presence of ``hot'' plasma, two observables in particular have been used to diagnose heating frequency in observations of \AR{} cores: the emission measure slope and the timelag. 

The emission measure distribution, $\mathrm{EM}(T)=\int\mathrm{d}h\,n^2$, provides the temperature distribution of the plasma in a single pixel and is a useful diagnostic for parameterizing the underlying heating mechanism. Many observational and theoretical studies have suggested that the ``cool'' portion of the \dem{} (i.e. leftward of the peak, $10^{5.5}\lesssim T\lesssim10^{6.5}$ K), can be described by $\mathrm{EM}(T)\sim T^a$ \citep{jordan_structure_1976,cargill_implications_1994,cargill_nanoflare_2004,warren_systematic_2012}. The so-called \textit{emission measure slope}, $a$, is an important diagnostic for assessing how often a single loop may be reheated and has been used by several workers to interpret \AR{} core observations in terms of both high and low frequency heating \citet[see Table 3 of][and references therin]{bradshaw_diagnosing_2012}. A similar scaling $\mathrm{EM}(T)\sim T^{-b}$ has been claimed for $T>\argmax_T\,\mathrm{EM}$ though this parameter is very sensitive to the temperature range over which the fit is performed \citep[see section 3.3.1 of][]{barnes_inference_2016-1}.

The ``cool'' \dem{} slope typically falls in the range $2<a<5$, with smaller (larger) values being signatures of low (high) frequency heating. Below $T(\mathrm{EM}_{max})$, \citet{cargill_implications_1994} noted that the \dem{} could be described by $\mathrm{EM}(T)\sim n^2\tau_{rad}$, where $\tau_{rad}\sim T^{1-\alpha}n^{-1}$ is the radiative cooling time. Furthermore, during radiative cooling, \citet{bradshaw_cooling_2010} found that $T\sim n^{\ell}$, with $\ell\approx1$ for long loops and $\ell\approx2$ for short loops. Combining these expressions, $\mathrm{EM}\sim T^{1+1/\ell-\alpha}$. Thus, assuming $\alpha=-1/2$ \citep[i.e. using the radiative losses of][]{rosner_dynamics_1978}, we find $a\approx2$ for short loops and $a\approx2.5$ for long loops in the case of single nanoflares, i.e. low frequency heating. Higher values of $a$ are expected as the heating frequency increases due to the \dem{} distribution becoming increasingly isothermal \citep{cargill_active_2014}. \authorcomment2{Add discussion of the rest of the modeling studies here, \citep[][and references therein]{mulu-moore_can_2011,bradshaw_diagnosing_2012,reep_diagnosing_2013,cargill_active_2014}}

Many observational studies of active regions have used the \dem{} slope to make conclusions about the heating frequency. \citet{tripathi_emission_2011} computed \dem{} from observations of inter-moss regions using data from the EUV Imaging Spectrometer \citep[EIS][]{culhane_euv_2007} onboard the \textit{Hinode} spacecraft \citep{kosugi_hinode_2007} and found $a\approx2.4$, consistent with low frequency nanoflares. \citet{warren_constraints_2011} constructed \dem{} distributions using observations of \AR{} cores from the Atmospheric Imaging Assembly \citep[AIA][]{lemen_atmospheric_2012} as well as the X-Ray Telescope \citep[XRT][]{golub_x-ray_2007} and EIS and made comparisons to \dem{} computed from field-aligned hydrodynamic models. \citeauthor{warren_constraints_2011} found $a\approx3.26$ and that their observed \dem{} were most consistent with high-frequency nanoflares though their high-frequency model could not reproduce the emission below $10^{6.5}$ K. Similarly, \citet{winebarger_using_2011} found good agreement between observed \dem{}, computed from XRT and EIS data, and a model \dem{}, computed from a steady heating model, in the temperature range $10^{6.3}<T<10^{6.7}$ K. However, the model \dem{} underestimated the emission in the temperature range $10^{6.1}<T<10^{6.3}$ K, suggesting there may be a low-frequency component to the heating as well. \citet{schmelz_cold_2012} computed \dem{} distributions for 8 different active regions observed by EIS and XRT and found 25\% had $a\sim4-5$, consistent with steady or high-frequency heating, while $\approx60\%$ had $1.91\le a\le2.84$, consistent with low-frequency nanoflares. While all of the studies listed so far have computed the \dem{} from a single pixel or a small area of the \AR{}, \citet{del_zanna_evolution_2015} calculated $a$ in every pixel of the \AR{} core from from AIA and EIS observations of NOAA 11193. \citeauthor{del_zanna_evolution_2015} found higher values of $a$ near the center of the core and lower values near the outer edge of the core, suggesting a distribution of heating frequencies across the \AR{}.

In general, deriving a \dem{} from observations is non-trivial and requires the use of an inversion method with a non-unique solution \citet[see][]{aschwanden_benchmark_2015}. Interpretation of these results is made difficult by several factors including multiple polluting structures along the LOS, uncertainties in the atomic data, and inadequate spectral coverage \citep{winebarger_defining_2012}.

\authorcomment1{Same as above but for timelags; then, thorough discussion of findings of authors using timelag method in the context of high/steady or low frequency heating}

\citet{viall_transition_2015,viall_survey_2017,bradshaw_patterns_2016,lionello_can_2016,winebarger_investigation_2016,winebarger_identifying_2018}

%\authorcomment1{Need to connect previous paragraph to frequency and how observables can be used to diagnose heating frequency; lead into impulsive v steady debate and cite MANY previous studies; these signatures not only provide a confirmation of the nanoflares existence, but contain information regarding nanoflare properties as well; }

In this paper, we carry out a series of nanoflare heating simulations in order to better understand how the frequency of impulsive heating events on a given strand is related to observable properties of the plasma, notably the emission measure slope and the timelag as derived from AIA observations. To carry out this study, we use a combination of magnetic field extrapolations, hydrodynamic models, atomic data, and advanced forward modeling to simulate EUV observations from SDO/AIA. The resulting forward modeled intensities can then be treated in the same manner as actual observations and we carry out the emission meaure and timelag analysis as such. \autoref{modeling} provides a detailed description of our forward modeling pipeline, including the parameterization of the heating model. In \autoref{results}, we show the results of the timelag (\autoref{timelags}) and emission measure (\autoref{em_slopes}) analysis as applied to our simulated intensity maps. \autoref{discussion} provides some discussion of our results and \autoref{conclusions} provides a summary and concluding remarks. Additionally, \autoref{nei} shows how to compute ion populations while accounting for non-equilibrium ionization and \autoref{timelag_details} details our efficient and scalable method for computing the timelag between intensity timeseries in two different channels of AIA.

This paper is the first in a series of papers concerned with constraining nanoflare heating properties through forward modeled observables and serves primarily to describe our forward modeling pipeline and lay out the simulation results. In \citetalias{barnes_understanding_2018-1}, we make detailed comparisons to observations and use the model results presented here to classify the heating frequency in each pixel of the observed \AR{}. Combined, these two papers demonstrate a novel method for using data and forward modeled observables to make sysematic predictions of heating properties in \AR{} cores.
